---
title: "R Notebook"
#output: html_notebook
output: html_document
---

```{r}
v <- c("apple", "banana", "cherry")
knitr::combine_words(v)
## apple, banana, and cherry
knitr::combine_words(v, before = "`", after = "'")
## `apple', `banana', and `cherry'
knitr::combine_words(v, and = "")
## apple, banana, cherry
knitr::combine_words(v, sep = " / ", and = "")
## apple / banana / cherry
knitr::combine_words(v[1])  # a single word
## apple
knitr::combine_words(v[1:2])  # two words
## apple and banana
knitr::combine_words(LETTERS[1:5])
## A, B, C, D, and E
```

Like Barley Bending  

Like barley bdeing  
  In low fields by the sea,  
  
  
```{r}
blogdown:::quote_poem(c("This line", "should be", "broken."))
## [1] "> This line  \nshould be  \nbroken."
```




```
Like barley bending
　In low fields by the sea,
Singing in hard wind
　Ceaselessly;

Like barley bending
　And rising again,
So would I, unbroken,
　Rise from pain;

So would I softly,
　Day long, night long,
Change my sorrow
　Into song.

--- Sara Teasdale
```




> 
>
> Like Barley Bending
>
> Like barley bending  
>　In low fields by the sea,  
Singing in hard wind  
>　Ceaselessly;
>
> Like barley bending  
>　And rising again,  
>So would I, unbroken,  
>　Rise from pain;
>
> So would I softly,  
>　Day long, night long,  
>Change my sorrow  
>　Into song.
>
> --- Sara Teasdale






## 4.13 


```{r}
#install.packages("devtools")
devtools::install_github("datalorax/equatiomatic")
```

```{r}
fit <- lm(mpg ~ cyl + disp, mtcars)
# show the theoretical model
equatiomatic::extract_eq(fit)
```


$$
\operatorname{mpg} = \alpha + \beta_{1}(\operatorname{cyl}) + \beta_{2}(\operatorname{disp}) + \epsilon
$$

```{r}
equatiomatic::extract_eq(fit, use_coefs = TRUE)
```

`r equatiomatic::extract_eq(fit, use_coefs = TRUE)`


$$
\operatorname{mpg} = 34.66 - 1.59(\operatorname{cyl}) - 0.02(\operatorname{disp}) + \epsilon
$$

$$ `r equatiomatic::extract_eq(fit, use_coefs = TRUE)` $$


```{r, mtcars-plots, results='asis'}
equatiomatic::extract_eq(fit, use_coefs = TRUE)
```

```{r, animation.hook="gifski"}
for (i in 1:2) {
  pie(c(i %% 2, 6), col = c('red', 'yellow'), labels = NA)
}
```





```{r grvi1}
DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]
  
  node [shape = rectangle]        
  rec1 [label = 'Step 1. Wake up']
  rec2 [label = 'Step 2. Write code']
  rec3 [label =  'Step 3. ???']
  rec4 [label = 'Step 4. PROFIT']
  
  # edge definitions with the node IDs
  rec1 -> rec2 -> rec3 -> rec4
  }", 
  height = 500)
```

```{r grviz2}
DiagrammeR::grViz("
  digraph graph2 {
  
  graph [layout = dot, rankdir = LR]
  
  # node definitions with substituted label text
  node [shape = oval]
  a [label = '@@1']
  b [label = '@@2']
  c [label = '@@3']
  d [label = '@@4']
  
  a -> b -> c -> d
  }
  
  [1]: names(iris)[1]
  [2]: names(iris)[2]
  [3]: names(iris)[3]
  [4]: names(iris)[4]
  ", 
  height = 100)
```

Mr. Dervieux. keep the social \ \ \ distance. keep the social \ \ \ distance.keep the social \ \ \ distance.keep the social \ \ \ distance.keep the social \ \ \ distance.keep the social \ \ \ 

keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. keep the social distance. 

<!-- I do not want \_italic text\_ here -->
<!-- \# This is not a heading -->

<!-- your comment -->


# Section heading {.unlisted .unnumbered}


# Appendix: All code for this report

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```

